Word Learning as Network Growth: A Cross-linguistic Analysis

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

\begin{abstract}
Stager and Werker (1997) first showed that chidlren's early ability to
distinguish similar sounds do not automatically translate into word
learning skills. Early explanations proposed that children may not be
able to encode subtile phonetic contrasts when learning novel word
meanings, thus suggesting a binary/discontinuous pattern of development.
However, later work has revealed (e.g., through using simpler testing
methods) that children do encode such contrasts, thus favoring a rather
probabilitic/continuous pattern of development. The present study
proposes a precise probabisitic model describing how development may
processd in a continuous fashion. The purpose of the model is to account
for previousely documented facts while providing new predictions. We
collected data from both preschool children and adults, and we show that
the model can explain various patterns of learning both within the same
age and across development. More generally, our work highlight the role
of computational modeling in advancing our understanding of development
through both organizing exsinting knowledge and generating new
principled hypotheses.

@@

Regardless of the exact explanation, it is generally accepted that by
around 17 m.o, chidlren succeed under the same circumstances (Werker,
Fennell, Corcoran, \& Stager, 2002). What could be the mechanism of
development? On one possible account, learning is stage-like: younger
children learn a single, underspecified representation of similar words
(e.g., ``bin''/``din''). Development occurs when children specify this
intial coarse reprepsentation and learn two distinct catgories. On an
other account, learning is continuous: distinct represetations are
learned even by younger children, but these representations are encoded
with higher uncertainty in youger children, leading to apparent failure
in relatively demanding tasks. Development is a continuous process
whereby the intinial noisy representations become more precise (see
also, Swingley, 2007).

Experimental evidence suggest a probabilsitic/continuous, rather than a
binary/discontinuous develomental scenario. On the one hand,
14-month-olds who typically fail in the original task succeed both when
an easier testing method is used (Yoshida, Fennell, Swingley, \& Werker,
2009), and when uncertainty is mitigated via disambiguating cues
(Dautriche, Swingley, \& Christophe, 2015; Thiessen, 2007). On the other
hand, adults show patterns of learning similar to those shown by
14-month-olds when the task is more challenging and when similarity
between words increases (Pajak, Creel, \& Levy, 2016; White, Yee,
Blumstein, \& Morgan, 2013).

Here talk about the continuous hypothesis a bit later here. after
introducing the experimental evidecne.

Also talk more about the major assumption of model, what is contiuous
about him? and what is the source of this hypothsis (swingley, Yoshida,
\ldots{})

In the light of these evidence, the purpose of the current work is to
propose a precise probabilsitc model of the Stager and Werker's task
where developmment is understood to proceed in a continuous fashion
across the lifespan. We use this model to both provide a unifying
account for documented experimental findings, and to make new
predicitions that have not been tested before. Using new data collected
from both preschool children and adults, we show that the model can
explain various patterns of learning both within the same age and across
development.

@@

We model the word learning task introduced by Stager \& Werker (1997),
and a testing method similar to the one used by Yoshida et al. (2009).
In this task, particiants are first exposed to the association between
pairs of nonesense words (e.g., ``lif''/``neem'') and pairs of objects.
After this exposure phase, participants perform a series of
two-alternative forced choices. In each testing trial, one of the two
sounds is uttered (e.g., ``lif'') and participants choose the
corresponding object from the two alternatives. An overview of the task
is shown in Figure~@ref(fig:task).

@@

Our model consists of a set of variables describing the general process
of spoken word recognition in a referential situation. These variables
are related in a way that refelects the simple generative scenario
represented graphically in Figure~@ref(fig:model). When a speaker utters
a sound in the presence of an object, the observer assumes that the
object \(o\) activated the concept \(C\) in the speaker's mind. The
concept prompted the cooresponding label \(L\). Finally, the label was
physically instantiated by the sound \(s\).

A similar probabilsitic structure was used by Lewis \& Frank (2013) to
model concept learning, and by Hofer \& Levy (2017) to model spoken word
learning. However, the first study assumed that the sounds are heard
unambiguousely, and the second assumed the concepts are observed
unambiguously. In our model, we made the more reaistic assumption of
ambiguity at the level of both the sounds and the objects. For
simplicity, we assume that the probability of membership of objects and
sounds to concepts and labels, respectively, are normally distributed:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
one-to-one mappings between concepts and labels, and that observers have
successfully learned these mappings during the exposure phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
\]

@@

During the testing phase, participants are presented with one target
sound \(s_T \in\{s_1, s_2\}\) and the two objects \(o_1\) and \(o_2\)
presented during the learning phase. In order to make a choice, we
determine which object is more probable under the target sound \(s_T\),
in other words, we compare the the probabilities \(P(o_1|s_T)\) and
\(P(o_2|s_T)\). The values of these probabilities can be computed by
summing over all possible concepts and labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
The joint probability \(P(o, C, L, s)\) is obtained by factoring the
bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
which could be tansformed using Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
concept prior probability is uniformly ditributed, we obtain the
following expression, where all conditional dependencies have been
defined in the previous sub-section.

\begin{equation}
P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
\end{equation}

From the general expression (1) we derive the exact analytical formula
which expresses the probability of accurate responses in the testing
phase (Figure 1).

@@

We provide an intuitive illustration of how this probabilistic account
explain patterns of learning and development in Figure XX. Low accuracy
in word learning occurs when the perceptual distance between the labels
is small relative to the uncertainty with wich these labels are encoded.
For example, in Stager and Werker's orginal experiment, children are
supposed to associate lable 1 (``bih'') and label 2 (``dih'') with
object 1 and object 2, respectively. Though children could learn that
the label ``bih'' is a better match to object 1 than ``dih'', they could
still judge the sound ``dih'' as a plausible instance of the lable
``bih'', thanks to the relatively large variance/tolerance of the
encoding.

Accuracy is high when the perceptual distance between the labels is
large relative to the uncertainty of their encoding. Thus, improvement
can occur in the same developmental stage if the perceptual distance of
the labels is enhanced either through using different-sounding labels
(e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or through
using additional disambiguating cues (e.g., Thiessen, 2007). Accuracy
improves over development because the encoding's uncertainty itself is
reduced.

In order to have a more quantitative understanding of the mdoel, we
simulate the values of the predicted accuracy (Expression 2) as a
function of the perceptual distance between the sounds \(\Delta s\). We
used as parameters the two remaning variables, i.e., the visual distance
between the semantic referents \(\Delta o\) and the standard deviation
of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
simulation, have similar values, i.e.,
\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
Figure 3.

@@

\caption{\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds. Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations. Panels represent graphs using different values of the visual distance between the objects.}\label{fig:simulation}
\end{figure*}
\end{CodeChunk}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
  accurate responses increases as a function of \(\Delta s\). This
  pattern accounts for the fact that similar sounds are generally more
  challenging to learn than different sounds for both chidlren (Stager
  \& Werker, 1997) and adults (Pajak et al., 2016).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
  when the representational noise (characterized with \(\sigma\))
  decreases. This fact may explain development, i.e., youger children
  have noisier representations (Swingley, 2007; Yoshida et al., 2009),
  which leads to lower word recognition accuracy, especially for similar
  sounding words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
  with the visual distance between the semantic referents \(\Delta o\).
  This is a new predcition that our model makes. Previous work studied
  the effect of several bottom-up and top-down properties in
  disambiguating similar sounding words (Dautriche et al., 2015; Fennell
  \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007), but no
  previous study tested the effect of the visual distance between the
  semantic referents.
\end{enumerate}

@@

\caption{\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development. Accuracy experesses the extent to which a given sound instance indicates a unique category. The values vary between 0.5 (total overlap) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

In this experiment, we tested participants in the word learning task
introduced above (Figure 1). We explored all three parameters of the
model. Both the sound similarity (\(\Delta s\)) and object similarity
(\(\Delta o\)) were varied simulataneousely in a within-subject design.
Besides, two age groups (preschool children and adults) were tested on
the same task to explore whether development can be characteized with
the degree of uncertainty, \(\sigma\), in the probabilsitic
representations.

@@

We planned to recruit a sample of 60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. So far, we
collected data from N=47 children (mean age= months, F=). An additional
28 children participated but were removed from analyses because they
were not above chance on the catch trials (as was specified in the
pre-registration\footnote{https://osf.io/jrh38/}). We also collected a
planed sample of N=30 adults on Amazon Mechanical Turk. N=2 adult
participants were excluded because of low scores on the catch trials
(see pre-registration).

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
generated three kinds of sound pairs which varied in their degree of
similarity to English speakers: 1) ``different'': ``lif''/``neem'' and
``zem''/``doof'', 2) ``intermediate'': ``aka''/``ama'' and
``ada''/``aba'', and 3) ``similar'' non-English minimal pairs:
``ada''/``a\textipa{d\super h}a'' (in hindi) and
``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).

As for the objects, we used the Dynamic Stimuli javascript
library\footnote{https://github.com/erindb/stimuli} which allowed us to
generate objects in four different categories: ``tree'', ``bird'',
``bug'', and ``fish''. These categories are supposed to be naturally
occuring kinds that might be seen on an alien planet. In each category,
we generated ``different'', ``intermediate'' and ``similar'' levels of
similarity by manipuating a continuous property controling features of
the category's shape (e.g, body strech and head fatness).

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and objcet pair
on a 7-point scale. We computed averge ratings across partcipants, and
we normalized the data so that the values vary between 0 to 1. Results
are shown in Figure XX, for each stimuli group. This data will be used
in the models as the perceptual distance of sound pairs (\(\Delta s\))
and object pairs (\(\Delta o\)).

@@

Each age group saw only two of the three levels of similarity described
in the previous sub-section: ``different'' vs. ``intermediate'' for
preschoolers, and ``intermediate'' vs. ``similar'' for adults. The
experiment consisted of four conditions which involved, each, one pair
of sounds-objects associations. These conditions were constructed by
crossing the sound's degree of similarity with the object's degree of
similarity leading to a 2x2 factorial design in each age group. Besides
the 4 conditions, we also tested participants on a fifth catch condition
which was similar in its stucture to the other ones, but was used only
to select participant who were able to follow the instructions and show
minimal learning.

@@

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial.

The procedure for preschoolers and adults were identical except that
preschoolers were accompagnied by an experimenter and used a tablet,
whereas adults used their local computers to complete the experiment
online.

@@

Discuss Hofer \& Levy, 2017, and Fourtassi \& Frank, 2017

>>>>

\begin{abstract}
Stager and Werker (1997) first showed that chidlren's early ability to
distinguish similar sounds do not automatically translate into word
learning skills. Early explanations proposed that children may not be
able to encode subtile phonetic contrasts when learning novel word
meanings, thus suggesting a discontinuous/stage-like pattern of
development. However, later work has revealed (e.g., through using
simpler testing methods) that children do encode such contrasts, thus
favoring a rather a continuous pattern of development. The present study
proposes a precise probabisitic model describing how development may
processd in a continuous fashion. The purpose of the model is to account
for previousely documented facts while providing new predictions. We
collected data from both preschool children and adults, and we show that
the model can explain various patterns of learning both within the same
age and across development. Our work highlight the role of computational
modeling in advancing our understanding of development through both
organizing exsinting knowledge and generating new principled hypotheses.

@@

Regardless of the exact explanation, it is generally accepted that by
around 17 m.o, children succeed in the same task (Werker, Fennell,
Corcoran, \& Stager, 2002). What could be the mechanism of development?
Early acccounts assumed--whether implcitly or explicitly-- that children
encode words in a binary way: they either fail or succeed in encoding
the relevant phonetic details (simulataneousely with the meanings). This
account suggested a discontinuous/stage-like pattern of development
whereby younger children fail to encode the contrastive phonetic detail,
whereas older children succeed.

Nevertheless, subsequent findings suggest otherwise. On the one hand,
14-month-olds--who typically fail in the original task--succeed when an
easier \emph{testing} method is used, even under the same
\emph{learning} conditions (Yoshida, Fennell, Swingley, \& Werker,
2009). They also succeed when uncertainty is mitigated via
disambiguating cues (e.g., Thiessen, 2007). On the other hand, adults
show patterns of learning similar to those shown by 14-month-olds when
the task is more challenging and when similarity between words increases
(Pajak, Creel, \& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).

These evidence point towards another scenario, where the representations
are encoded in a probablistic (rather than binary) way, and where
development is continuous, rather than stage-like (Hofer \& Levy, 2017;
Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009). On this
account, correct represetations are learned early in development, but
these representations are encoded with higher uncertainty in youger
children, leading to apparent failure in relatively demanding tasks.
Development is a continuous process whereby the intinial noisy
representations become more precise. Crucially, more precise
representation are still imperfect, as low accuracy learning can be
obtained even with adults when the sounds are subtle enough, e.g.,
non-native sounds (Pajak et al., 2016).

We provide an intuitive illustration of how such an account explains
patterns of learning and development in Figure \ref{fig:illus}. We
observe low accuracy in word learning when the perceptual distance
between the labels is small relative to the uncertainty/tolerance with
wich these labels are encoded. For example, in Stager and Werker's
orginal experiment, children are supposed to associate lable 1 (``bih'')
and label 2 (``dih'') with object 1 and object 2, respectively. Though
children could learn that the label ``bih'' is a better match to object
1 than ``dih'', they could still judge the sound ``dih'' as a plausible
instance of the lable ``bih'', thanks to the relatively large tolerance
of the encoding.

Accuracy in word learning increases when the perceived distance between
the labels is large relative to the tolerance of their encoding. This
improvement can occur in the same developmental stage if the perceptual
distance between labels is enhanced through using different-sounding
labels (e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or
through using contextual cues (Rost \& McMurray, 2009; Thiessen, 2007).
Besides, accuracy can improve across development through the refinement
of the encoding, i.e., if the uncertainy of the encoding decreases.

Building on this intuition, the current work proposes a precise
probabilsitc model, which we use to both account for previous
experimental findings, and to make new predicitions that have not been
tested before. Using new data collected from both preschool children and
adults, we show that the model can explain various patterns of learning
both within the same age and across development.

\caption{\label{fig:illus} An illustration of the probabilsitic account using simulated data. Words are category distributions over the perceptual space, encoded with different degrees of uncertainty. Accuracy experesses the extent to which a given sound instance indicates a unique underlying category. The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

We model the word learning task introduced by Stager \& Werker (1997),
and a testing method similar to the one used by Yoshida et al. (2009).
In this task, particiants are first exposed to the association between
pairs of nonesense words (e.g., ``lif''/``neem'') and pairs of objects.
After this exposure phase, participants perform a series of
two-alternative forced choices. In each testing trial, one of the two
sounds is uttered (e.g., ``lif'') and participants choose the
corresponding object from the two alternatives. An overview of the task
is shown in Figure \ref{fig:task}.

@@

Our model consists of a set of variables describing the general process
of spoken word recognition in a referential situation. These variables
are related in a way that refelects the simple generative scenario
represented graphically in Figure \ref{fig:model}. When a speaker utters
a sound in the presence of an object, the observer assumes that the
object \(o\) activated the concept \(C\) in the speaker's mind. The
concept prompted the corresponding label \(L\). Finally, the label was
physically instantiated by the sound \(s\).

A similar probabilsitic structure was used by Lewis \& Frank (2013) to
model concept learning, and by Hofer \& Levy (2017) to model spoken word
learning. However, the first study assumed that the sounds are heard
unambiguousely, and the second assumed the concepts are observed
unambiguously. In our model, we assume there to be ambiguity at the
level of both the labels and the concepts. For simplicity, we assume
that the probability of membership of objects and sounds to concepts and
labels, respectively, are normally distributed:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] Finally, we assume
there to be one-to-one mappings between concepts and labels, and that
observers have successfully learned these mappings during the exposure
phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
\]

@@

During the testing phase (Figure \ref{fig:task}), participants are
presented with one target sound \(s_T \in\{s_1, s_2\}\) and with both
objects \(o_1\) and \(o_2\). In order to make a choice, we need to
determine which object is more probable under the target sound \(s_T\).
In other words, we need to compare the probabilities \(P(o_1|s_T)\) and
\(P(o_2|s_T)\). The values of these probabilities can be computed by
summing over all possible concepts and labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
The joint probability \(P(o, C, L, s)\) is obtained by factoring the
Bayesian network in (Figure \ref{fig:model}):
\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which could be tansformed using
Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
concepts' prior probability is uniformly
ditributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in the Experiment below.},
we obtain the following expression, where all conditional dependencies
are now well defined:

\[
P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
\]

From this general expression we derive the exact analytical formula,
which expresses the probability of accurate responses in the testing
phase of the task:

@@

In order to have a more quantitative understanding of the model, we
simulate the values of the predicted accuracy (Expression 1) as a
function of the perceptual distance between the sounds \(\Delta s\). We
used as parameters the two remaning variables, i.e., the visual distance
between the semantic referents \(\Delta o\) and the standard deviation
of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
simulation, are assumed to have similar values, i.e.,
\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
Figure \ref{fig:simulation}.

@@

\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase, as a function the perceptual distance between the sounds. Colors indicate different values of the standard deviation which we assume is common to both the labels' and concepts' probabilistic representations. Panels represent graphs using different values of the visual distance between the objects.}\label{fig:simulation}
\end{figure*}
\end{CodeChunk}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
  accurate responses increases as a function of \(\Delta s\). This
  pattern accounts for the fact that similar sounds are generally more
  challenging to learn than different sounds for both chidlren (Stager
  \& Werker, 1997) and adults (Pajak et al., 2016).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
  when the representational uncertainty (characterized with \(\sigma\))
  decreases. This fact may explain development, i.e., youger children
  have noisier representations (see Swingley, 2007; Yoshida et al.,
  2009), which leads to lower word recognition accuracy, especially for
  similar-sounding words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
  with the visual distance between the semantic referents \(\Delta o\).
  This is a new predcition that our model makes. Previous work studied
  the effect of several bottom-up and top-down properties in
  disambiguating similar sounding words (Dautriche, Swingley, \&
  Christophe, 2015; Fennell \& Waxman, 2010; Rost \& McMurray, 2009;
  Thiessen, 2007), but no previous study tested the effect of the visual
  distance between the semantic referents.
\end{enumerate}

@@

@@

In this experiment, we tested participants in the word learning task
introduced above (Figure \ref{fig:task}). We explored all three
parameters of the model. In particular, both the sound similarity
(\(\Delta s\)) and object similarity (\(\Delta o\)) were varied
simulataneousely in a within-subject design. Besides, two age groups
(preschool children and adults) were tested on the same task to explore
whether development can be characteized with the uncertainty parameter,
\(\sigma\), in the probabilsitic representations.

@@

We planned to recruit a sample of 60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. So far, we
collected data from N=47 children (mean age= months, F=). An additional
28 children participated but were removed from analyses because they
were not above chance on the catch trials (as was specified in the
pre-registration\footnote{https://osf.io/jrh38/}). We also collected a
sample of N=20 adults on Amazon Mechanical Turk (this is a pilot, I will
plan for 60 participants). N=2 adult participants were excluded because
of low scores on the catch trials (see pre-registration). (I still need
to write the code that derives these numbers directly from the data).

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
generated three kinds of non-sense word pairs which varied in their
degree of similarity to English speakers: 1) ``different'':
``lif''/``neem'' and ``zem''/``doof'', 2) ``intermediate'':
``aka''/``ama'' and ``ada''/``aba'', and 3) ``similar'' non-English
minimal pairs: ``ada''/``a\textipa{d\super h}a'' (in hindi) and
``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).

As for the objects, we used the Dynamic Stimuli javascript
library\footnote{https://github.com/erindb/stimuli} which allowed us to
generate objects in four different categories: ``tree'', ``bird'',
``bug'', and ``fish''. These categories are supposed to be naturally
occuring kinds that might be seen on an alien planet. In each category,
we generated ``different'', ``intermediate'' and ``similar'' pairs by
manipuating a continuous property controling features of the category's
shape (e.g, body strech or head fatness).

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and objcet pair
on a 7-point scale. We processed the resulting data so that it can be
used in the model. We normalized the values with respect to the most
distant level, and we scaled them within the range {[}0,1{]}. Processed
data are shown in Figure \ref{fig:stim}, for each stimuli group. This
data will be used in the models as the perceptual distance of sound
pairs (\(\Delta s\)) and object pairs (\(\Delta o\)).

@@

Each age group saw only two of the three levels of similarity described
in the previous sub-section: ``different'' vs. ``intermediate'' for
preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
this choice because, on the one hand, adults were at ceiling with
``different'' sounds, and on the other hand, children were at chance
with the ``similar'' sounds. That said, this difference in the level of
similairty is accounted for in the model through using the appropriate
perceptual distance for each age group (Figure \ref{fig:stim})

The experiment consisted of four conditions which involved, each, one
pair of sounds-objects associations. These conditions were constructed
by crossing the sound's degree of similarity with the object's degree of
similarity leading to a 2x2 factorial design in each age group. Besides
the 4 conditions, we also tested participants on a fifth catch condition
which was similar in its stucture to the other ones, but was used only
to select participants who were able to follow the instructions and show
minimal learning.

@@

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial. The procedure for preschoolers and adults were identical
except that preschoolers were accompagnied by an experimenter and used a
tablet, whereas adults used their local computers to complete the
experiment online.

@@
